\subsection*{References}
\begin{frame}[t]
  % \small 
  \tiny % is really really tiny!
    \begin{itemize}
    \item{
      B. Kirk, J. Peterson, R. Stogner and G. Carey, ``libMesh: a C++
      library for parallel adaptive mesh refinement/coarsening
      simulations,''  \emph{Engineering with Computers}, vol.~22, no.~3--4, p.~237--254, 2006.
      }
     \end{itemize}
     \rule{\textwidth}{1pt}
     \begin{itemize}
\item{
J.~W. Peterson, G.~F. Carey, and B.~T. Murray, ``{Multi-Resolution Simulation
  of Double-Diffusive Convection in Porous Media},'' {\em Int. J. Numer. Meth.
  for Heat \& Fluid Flow}, to appear, Nov.\ 2009 issue.
}
    \item{
        J.~Biermann, O.~von Estorff, S.~Petersen, C.~Wenterodt,      
        ``Higher order finite and infinite elements for the solution of Helmholtz problems,''
        \emph{Computer Methods in Applied Mechanics and Engineering}, vol.~198,
        no.~13--14, p.~1171--1188, 2009.
      }
    \item{
      B.~Kirk, ``A Multidimensional Thermal Analysis to Assess Modeling Error in High-Speed
      Wind Tunnel Heat Transfer Data Reduction Schemes,''
      \emph{AIAA Journal of Thermophysics and Heat Transfer}, vol.~23, no.~1, p.~186--191, 2009.       
    }
  \item{
      Benjamin S. Kirk, Graham F. Carey, 
      ``Development and Validation of a SUPG Finite Element Scheme for the Compressible
      Navier-Stokes Equations using a Modified Inviscid Flux Discretization,''
      \emph{Int. J. Numer. Meth. Fluids}, vol.~57, no.~3, p.~265--293, 2008.
    }
  \item{R. Stogner and G. Carey, ``$C^1$ macroelements in adaptive finite
      element methods,''
      \emph{Int. J. Num. Meth. Eng.}, vol.~70, no.~9, p.~1076--1095, 2007.
      }
  \item{
    M.~F.~Barone, I.~Kalashnikova, D.~J.~Segalman, H.~K.~Thornquist,
    ``Stable Galerkin reduced order models for linearized compressible flow,''
    \emph{Journal of Computational Physics}, vol.~228, no~6, p.~1932--1946 2009.}

  \item{
      M.~Piccinelli, L.~Botti, B.~Ene-Iordache, A.~Remuzzi,
      A.~Veneziani, L.~Antiga,
      ``Link between vortex structures and voronoi diagram in cerebral aneurysms,''
      \emph{Journal of Biomechanics}, vol.~41, Supplement 1, p.~S12, 2008.
    }
    \item{
        F.~Galbusera, M.~Cioffi, and M.~T.~Raimondi, 
        ``An in silico bioreactor for simulating laboratory experiments in 
        tissue engineering,'' \emph{Biomedical Microdevices}, vol.~10, no.~4, p.~547--554, August, 2008.
      }
  \item{
      M.~Anderson, J.-H.~Kimn,
      ``A numerical approach to space-time finite elements for the wave equation,''
      \emph{Journal of Computational Physics}, vol.~226, no.~1, p.~466--476, 2007.
    }

    \end{itemize}
\end{frame}

% \subsection*{Was anyone else able to get some work done with it?}
% \begin{frame}
%   \small
%   \begin{itemize}
%   \item{
%     M.~F.~Barone, I.~Kalashnikova, D.~J.~Segalman, H.~K.~Thornquist,
%     ``Stable Galerkin reduced order models for linearized compressible flow,''
%     \emph{Journal of Computational Physics}, vol.~228, no~6, p.~1932--1946 2009.}

%   \item{
%       M.~Piccinelli, L.~Botti, B.~Ene-Iordache, A.~Remuzzi,
%       A.~Veneziani, L.~Antiga,
%       ``Link between vortex structures and voronoi diagram in cerebral aneurysms,''
%       \emph{Journal of Biomechanics}, vol.~41, Supplement 1, p.~S12, 2008.
%     }

%   \item{
%       M.~Anderson, J.-H.~Kimn,
%       ``A numerical approach to space-time finite elements for the wave equation,''
%       \emph{Journal of Computational Physics}, vol.~226, no.~1, p.~466--476, 2007.
%     }

%   \end{itemize}
% \end{frame}
